Asteroseismology of GD358 with complex C/O core profiles

### 2016-02-15 msnew.tex
Partial abstract added

\begin{abstract}
We report on ......
\end{abstract}

@@

In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}. We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models. Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058). It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114. Pinning down the proper effective temperature of each star is challenging. To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained asteroseimically. At best we can contrast blue edge versus red edge objects.

Numerical experiments of the type presented in section \ref{refinedfits} \citep{Bischoff-Kim15} have shown that, consistent with the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur. Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}. We refrained from doing this in the present study because we wanted to compare our results with previous studies of DBVs. It is unclear how much of an effect on structure parameters a change in parameterization would have.

>>>>

\begin{abstract}
We report on the analysis of XXXX numbers of hours of data collected on the pulsating helium atmosphere white dwarf star, GD358. From this data set added to archival data, we extract 15 frequencies, adding 4 modes to the 11 modes known previously. We present evidence that the 15 modes are $\ell=1$ modes, 13 of which belong to a consecutive sequence in $k$. We use models that include parameterized, complex carbon and oxygen core composition profiles to fit the periods.
\end{abstract}

@@

In this study, we varied the parameters that have traditionally been varied in this type of asteroseismic fitting, so that we can place our results side by side with other studies of DBVs, including KIC 8626021 \citep{Bischoff-Kim14}, EC200058 \citep{Bischoff-Kim11a}, and CBS114 \citep{Metcalfe05a}. We now have 4 DBVs that were the object of asteroseismic fitting that used a consistent set of models. Unfortunately, GD358 does not fit neatly into the trend (neither does EC20058). It is true, however that the two blue edge objects (EC20058 and KIC 8626021) have thinner helium layers ($M_{\rm He}=-6.10$ and $-7.90$ respectively) than the red edge stars ($M_{\rm He}=-5.40$ for GD358 and $-5.94$ for CBS114. Pinning down the proper effective temperature of each star is challenging. To be fully consistent, it is best to use the asteroseismic values, even if effective temperature is not strongly constrained asteroseimically. At best we can contrast blue edge versus red edge objects.

Numerical experiments of the type presented in section \ref{refinedfits} have shown that, consistent with the theory of non-radial oscillations, the shapes of the transition zones matter as much as where the transition zones occur \citep{Bischoff-Kim15}. Modern asteroseismic fitting vary parameters attached to the shape of transition zones \citep{Giammichele15}. We refrained from doing this in the present study because we wanted to compare our results with previous studies of DBVs. It is unclear how much of an effect on structure parameters a change in parameterization would have.
